Misspecification Demonstration

### 2022-07-26 misspecification_study/misspec_demo.Rmd
add liz retro plots

source(file.path(here(), "common_code", "make_basic_info.R"))
source(file.path(here(), "common_code", "bias_data.R"))
```

@@

The catch and index four panel plots all look good for UR_em4.

@@

The problematic diagnostic is the NAA 4 panel plots, show below for ages 1 and 8 as well as the stacked barplot of residuals.

![NAA age 1 4 panel](UR_em4/plots_png/diagnostics/NAA_4panel_1.png)
![NAA age 8 4 panel](UR_em4/plots_png/diagnostics/NAA_4panel_8.png)
![NAA residuals stacked barplot](UR_em4/plots_png/diagnostics/NAA_res_barplot_stacked.png)

>>>>

source(file.path(here(), "common_code", "make_basic_info.R"))
source(file.path(here(), "common_code", "bias_data.R"))
source(file.path(here(), "common_code", "fn_retro_par_estimates.R"))
```

@@

The catch and index four panel plots all look good for UR_em4. The problematic diagnostic is the NAA 4 panel plots, show below for ages 1 and 8 as well as the stacked barplot of residuals.

@@

![NAA age 1 4 panel](UR_em4/plots_png/diagnostics/NAA_4panel_1.png)

![NAA age 8 4 panel](UR_em4/plots_png/diagnostics/NAA_4panel_8.png)

![NAA residuals stacked barplot](UR_em4/plots_png/diagnostics/NAA_res_barplot_stacked.png)

Use Liz's plot.retro.pars function to examine the stability of parameter estimates across the retrospective peels. For now just look at under-reported catch case with estimation model 4 (UR_em4).

```{r lizretro}
# again had to run this in console because could not get it to knit
#em8lr.dir <- file.path(here(), "misspecification_study", "UR_em4", "liz_retro_plots")
#plot.retro.pars(m=em_fits[[8]][[1]], yr.plot.start=2005, od=em8lr.dir, save.name="UR_em4", 
#  plot.f='png' )
```

None of the retrospective plots show a strong pattern. The unusual result of nearly all the NAA log_Deviations being below zero holds for all the peels.

![fleet selectivity](UR_em4/liz_retro_plots/UR_em4._fleet.sel.full.plot.png)

![index selectivity](UR_em4/liz_retro_plots/UR_em4._ind.sel.full.plot.png)

![NAA log deviations](UR_em4/liz_retro_plots/UR_em4._naa.devs.full.plot.png)

![Survey catchability](UR_em4/liz_retro_plots/UR_em4._q.full.plot.png)
